Insert your title here

### 2018-08-13 sect4-lower-bounds.tex

In order to develop an algorithm for the \textsc{Node Degree Relaxation}, we derive some optimality conditions of its single-source version.
Thus, let $S=\left\{v_1\right\}$ and $V\setminus S=\left\{v_2,\ldots,v_n\right\}$, where $\delta_G(v_2)\geq\delta_G(v_3)\geq\dots\geq\delta_G(v_n)$,
and denote $d_i=\delta_G(v_i)$ ($i=1,\ldots,n$).
Let $\tau_i=\tau\left(T[i],\{v_i\}\right)$ denote the broadcast time of node $v_i$ in the subtree $T[i]$ of $T$ rooted at $v_i$.
The broadcast time $\tau\left(V,\{v_1\}\right)$ is hence no less than the sum of the time $\lceil\log\beta(v_i)\rceil$ it takes to inform $v_i$,
and the subsequent time $\tau_i$ needed to inform all nodes in $T[i]$.
Consequently, if $T$ is an optimal broadcast tree,
\begin{equation}
  \tau\left(V,\{v_1\}\right)=\max\left\{\lceil\log\beta(v_i)\rceil+\tau_i: i=2,\ldots,n\right\}. \label{eq:tau}
\end{equation}

>>>>

In order to develop an algorithm for the \textsc{Node Degree Relaxation}, we derive some optimality conditions of its single-source version.
Thus, let $S=\left\{v_1\right\}$ and $V\setminus S=\left\{v_2,\ldots,v_n\right\}$, where $\delta_G(v_2)\geq\delta_G(v_3)\geq\dots\geq\delta_G(v_n)$,
and denote $d_i=\delta_G(v_i)$ ($i=1,\ldots,n$).

Consider an optimal communication tree $T$. That is, $T$ is a subtree of $G$ rooted at the unique source $v_1$ such that
$\tau\left(G,\{v_1\}\right)=\tau\left(T,\{v_1\}\right)$.
Let $\tau_i=\tau\left(T[i],\{v_i\}\right)$ denote the broadcast time of node $v_i$ in the subtree $T[i]$ of $T$ rooted at $v_i$.
The optimal broadcast time $\tau\left(T,\{v_1\}\right)$ is hence no less than the sum of the time $\lceil\log\beta(v_i)\rceil$ it takes to inform $v_i$,
and the subsequent time $\tau_i$ needed to inform all nodes in $T[i]$.
Taking the largest of all such lower bounds, we get:
\begin{equation}
  \tau\left(T,\{v_1\}\right)=\max\left\{\lceil\log\beta(v_i)\rceil+\tau_i: i=2,\ldots,n\right\}. \label{eq:tau}
\end{equation}
